Software Architectures to Integrate Workflow Engines in Science Gateways

### 2016-04-26 paper.tex
Merge remote-tracking branch 'glatard/master'
# Conflicts:
#	paper.tex

The pool architecture is overall the most scalable, which is not a
surprise since it was designed precisely for scalability. Tight
integration is the least scalable and all the other architectures
perform the same. The overall scalability score, however, should not
mask the unique characteristics of architectures regarding this
criterion. Nested workflows are the only architecture that can easily
accommodate distributed workflow execution, which can be critical in
some cases. At the same time, the scheduling constraints created by
the sub-tasking and nested workflow architectures could well become
showstoppers depending on the type of the targeted
infrastructure. Non-reliable infrastructures, for example, could
hardly cope with workflow engines being wrapped in computing tasks as
done in sub-tasking. The availability of multiple engine instances
could also become a critical feature for science gateways with
important workloads, which would favor sub-tasking and pool.

>>>>

The pool architecture is overall the most scalable, which is not a
surprise since it was designed precisely for scalability. Tight
integration is the least scalable and all the other architectures
perform the same. The overall scalability score, however, should not
mask the unique characteristics of architectures regarding this
criterion. Nested workflows are the only architecture that can easily
accommodate distributed workflow execution, which can be critical in
some cases. At the same time, the scheduling constraints created by
the sub-tasking and nested workflow architectures could well become
showstoppers depending on the type of the targeted
infrastructure. Non-reliable infrastructures, for example, could
hardly cope with workflow engines being wrapped in computing tasks as
done in sub-tasking \note{Marc-e}{free for all? WE dev involved?}. The availability of multiple engine instances
could also become a critical feature for science gateways with
important workloads, which would favor sub-tasking and pool.
